A Wide-Coverage Symbolic Natural Language Inference System

### 2019-07-27 paper2018/paper.tex
fix
aff

\usepackage{stmaryrd}
\usepackage{enumitem}
\usepackage{newunicodechar}
\input{PaperTools/latex/newunicodedefs}
\usepackage{hyperref}

\title{A Wide-Coverage Symbolic Natural Language Inference System}

% - Two-phase system (Dyn semantics from theorem proving)
% - Anaphora (as in Jolli paper) --- but this is the first time that this is done for FraCas.
% - Multiple readings
% - Threshold-based interpretation of (some) adjectives + Linear arithmetic proofs
% - New handling of prepositions and adverbs
% - Definites handled by adding an assumption at the top-level. (instead as inline existential) -- Enabled by dyn. semantics
% - Plurals/Quantifiers improved
% - Genders are properties of nouns
% - Handling of comparatives (with threshold BUT not those of adjectives), relying largely on the dyn. semantic system

@@

\paragraph{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described in
\citet{bernardy_jolli}. More details are given in the next
section.

>>>>

\usepackage{stmaryrd}
\usepackage{enumitem}
\usepackage{newunicodechar}
\input{PaperTools/latex/newunicodedefs}
\usepackage{hyperref}
\usepackage{url}
\aclfinalcopy % Uncomment this line for the final submission
\title{A Wide-Coverage Symbolic Natural Language Inference System}
\author{Jean-Philippe Bernardy\\
	Department of Philosophy, Linguistics \\ and Theory of Science\\
University of Gothenburg \\
\hskip -0.2in	{\tt jean-philippe.bernardy@gu.se} \\\And
	Stergios Chatzikyriakidis \\
	Department of Philosophy, Linguistics \\ and Theory of Science\\
University of Gothenburg \\
\hskip 0.4in	{\tt stergios.chatzikyriakidis@gu.se} \\}
% - Two-phase system (Dyn semantics from theorem proving)
% - Anaphora (as in Jolli paper) --- but this is the first time that this is done for FraCas.
% - Multiple readings
% - Threshold-based interpretation of (some) adjectives + Linear arithmetic proofs
% - New handling of prepositions and adverbs
% - Definites handled by adding an assumption at the top-level. (instead as inline existential) -- Enabled by dyn. semantics
% - Plurals/Quantifiers improved
% - Genders are properties of nouns
% - Handling of comparatives (with threshold BUT not those of adjectives), relying largely on the dyn. semantic system

@@

\paragraph{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described in
\citet{anaphora}. More details are given in the next
section.
